Approximate State Abstraction

### 2016-01-30 paper/paper.tex

Consider a temporally heterogeneous \ac{MDP}, $M^T$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$. Note that $M^0 = M_G$ and $M^\infty = M_A$.

The value of a state in $M^T$ is defined by:
\begin{equation}
V_T(s) = \max_a \left| \mathcal{R}_T(s,a) + \gamma \sum_{s'} \mathcal{T}_T(s,a,s') V_{T-1}(s') \right|
\end{equation}

Similarly, the Q-value of state $s$ in $M^T$ for action $a$ is defined by:
\begin{equation}
Q(s, a) = \mathcal{R}_T(s,a) + \gamma \sum_{s'} \mathcal{T}_T(s,a,s') \max_{a'} Q(s',a')
\end{equation}

Where:
\begin{equation}
\mathcal{R}_T = \begin{cases}
\mathcal{R}_A& T > 0 \\
\mathcal{R}_G& \text{otherwise} \\
\end{cases}
\end{equation}

And:
\begin{equation}
\mathcal{T}_T = \begin{cases}
\mathcal{T}_A& T > 0 \\
\mathcal{T}_G& \text{otherwise} \\
\end{cases}
\end{equation}

\enote{Add something about weirdness of state spaces changing at $T=1$}

We proceed by induction on $T$ to show that:
\begin{equation}
\forall_{T, g \in \mathcal{S}_G, a} |Q_G(g, a) - Q_T(\epQ(g), a)| \leq \sum_{t=0}^{T+1} \epsilon \gamma^t
\end{equation}

% Base Case
\textit{Base Case:}

\enote{Fix this -- state spaces are the same for this case}

When T = 0, $Q^{\pi_G^*} = Q_0$, so it trivially follows that:
\begin{equation}
\forall_{g\in \mathcal{S_G}, a} |Q^{\pi_G^*}(g, a) - Q_T(\ep_{Q^*}(g), a)| \leq \sum_{t=0}^{0} \epsilon \gamma^t
\end{equation}

\enote{Add base case for $T=1$ since our value function is not well defined unless $T > 1$.}

% Inductive Case
\textit{Inductive Case:} \enote {For $T>1$}

We assume as our inductive hypothesis that:
\begin{equation}
\forall_{g \in \mathcal{S}_G, a} |Q^{\pi_G^*}(g, a) - Q_{T-1}(\epQ(g), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t\\
\end{equation}

>>>>

Let $Q_G : \mathcal{S}_G \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_G : \mathcal{S}_G \rightarrow \mathbb{R}$ denote the Q and value functions in the ground \ac{MDP}.

Let $Q_A  : \mathcal{S}_A \times \mathcal{A} \rightarrow \mathbb{R}$ and $V_A : \mathcal{S}_A \rightarrow \mathbb{R}$  stand for the Q and value functions in the abstract \ac{MDP}.

Let $X(s) = \{g \in \mathcal{S}_G | \epQ(g) = s\}$.

%Claim 1
\textbf{Claim 1 -- Q-Values in the abstract MDP, closely resemble those in the ground MDP:}
\begin{equation}
\label{eq:Q*Claim1}
\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_A(\epQ(s_G), a)| \leq \frac{\epsilon}{1-\gamma}
\end{equation}

Consider a temporally heterogeneous \ac{MDP}, $M^T = \langle \mathcal{S}_T, \mathcal{A}_G, \mathcal{R}_T, \mathcal{T}_T, \gamma \rangle$, parameterized by integer $T$, such that for the first $T$ time steps the reward function, transition dynamics and state space are those of the abstract MDP, $M_A$, and after $T$ time steps the reward function, transition dynamics and state spaces are those of the ground MDP, $M_G$.

Where:
\begin{equation}
\mathcal{S}_T = \begin{cases}
\mathcal{S}_G& T \leq 0 \\
\mathcal{S}_A& \text{o/w} \\
\end{cases}
\end{equation}

And:
\begin{equation}
\mathcal{R}_T(s,a) = \begin{cases}
\mathcal{R}_G(s,a)& T \leq 0 \\
\mathcal{R}_A(s, a)& \text{o/w} \\
\end{cases}
\end{equation}

And:
\begin{equation}
\mathcal{T}_T(s,a,s') = \begin{cases}
\mathcal{T}_G(s,a,s')& T \leq 0 \\
\underset{{g \in X(s)}}{\sum}\left[w(g)T_G(g, a, s')\right]& T = 1 \\
\mathcal{T}_A(s,a,s')& \text{o/w} \\
\end{cases}
\end{equation}

It follows that the Q-value of a state $s$ in $M^T$ for action $a$ is defined by:
\begin{equation}
Q_T(s, a) = 
\begin{cases}
	   Q_G(s, a) &  T=0\\
	   \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
	   \mathcal{R}_A(\epQ(s),a) + \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a') & \text{o/w}
\end{cases}
\end{equation}

We proceed by induction on $T$ to show that:
\begin{equation}
\forall_{T, s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t}
\end{equation}

% Base Case t=0
\textit{Base Case: $T = 0$}

When T = 0, $Q_T = Q_0$, so the result trivially follows.

% Base Case t=1
\textit{Base Case: $T = 1$}
\begin{align*}
&Q_1(s,a) = \underset{g \in X(s)}{\sum} \left[ w(g)Q_G(g,a) \right]\\
\end{align*}
Since all aggregated states have Q-values within $\epsilon$ of one another and $w(g)$ induces a convex combination.
\begin{align*}
&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_0(s_G, a)\\
&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_0(s_G, a)\\
&\text{Thus,}\\
&Q_1(s,a) \left| Q_{T}(s_A, a) - Q_0(s_G,a) \right| \leq \gamma\sum_{t=0}^{1}\epsilon \gamma^t
\end{align*}

% Inductive Case
\textit{Inductive Case: $T > 1$}

We assume as our inductive hypothesis that:
\begin{equation}
\forall_{s_G \in \mathcal{S}_G, a} |Q_0(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t\\
\end{equation}
